Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-04 paper/ms.tex
small changes to abstract and mispelling errors

\author[~J.~E. Forero-Romero and J. Mejia]{
\parbox[t]{\textwidth}{\raggedright 
Jaime E. Forero-Romero$^{1}$ and
Julian Mej\'ia$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
$^{2}$ --}

@@

\begin{abstract}
We use cosmological N-body simulations to find the characteristic mass
of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies at a
redshift of $z=3.1$. The method is based on matching the statistics
for the number density between mock and observed fields. The mock
catalogs are constructed using a simple model where a dark matter halo
can only host one LAE with a probability $f_{\rm occ}$ if its mass is
found withing a certain range mass range delimited by two threshold
values, $M_{\rm min}$ and $M_{\rm max}$. We find that the most of the models that
are consistent the observed cosmic variance statistics are those with
halo masses in the range $10.5 < \log_{10} M_{\rm  min}/hMsun < 11.5$
and $\log_{10} M_{\rm max}/\hMsun < 13.5$ with and occupation fraction
that scales as $f_{\rm occ}=$. We explore three additional constraints
to narrow down these range: the number of mocks consistent with 
observations, observational constraints on the occupation fraction and
the angular correlation function. The first two conditions narrow down
the space parameter to $M_{\rm min}=$ and $M_{\rm max}$, $f_{\rm occ}$. The angular
correlation function does not add a significant constraint due to the
cosmic variance in the small angular fields where this statistics has
been computed so far. We make available the mock data for the best
models in a public repository. Implications for galaxy formation
models? 
\end{abstract}

@@

In our model a dark matter halo can only host one or zero LAE. 
There are three parameters in the model that decide whether a halo can host a
galaxy or not: the lower and upper bouds for the mass range $M_{\rm min}<
M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
  occ}$ of such halos that effectively host a LAE. We do not assign a
luminosity to each each LAE. We are primaraly interested in
constraining the halo mass range hosting detectable LAEs under the
conditions defined by \cite{Yamada2012}. In what follows will describe by
the letter ${\mathcal M}$ a model defined by an specific choice of the
three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ y $f_{\rm occ}$.

@@

The measurementens presented in \citep{Yamada2012} do not present a
new measurement of the angular correlation function (ACF). However
\citep{Hayashino2004} performed such calculation on the LAEs observed
inthe densest field of SSA22.

>>>>

\author[~J.~E. Forero-Romero and J. Mejia]{
\parbox[t]{\textwidth}{\raggedright 
Jaime E. Forero-Romero$^{1}$ and
Julian Mej\'ia$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
$^{2}$ Departamento de Astronom\'{i}a, Universidad de Chile, Camino el Observatorio 1515, Santiago, Chile}

@@

\begin{abstract}
We use cosmological N-body simulations to find the characteristic mass
of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies at a
redshift of $z=3.1$. The method is based on matching the statistics
for the number density between mock and observed fields. The mock
catalogs are constructed using a simple model where a dark matter halo
can only host one LAE with a probability $f_{\rm occ}$ if its mass is
found withing a certain range mass range delimited by two threshold
values, $M_{\rm min}$ and $M_{\rm max}$. We find that the most of the models that
are consistent the observed cosmic variance statistics are those with
halo masses in the range $10.5 < \log_{10} M_{\rm  min}/hMsun < 11.5$
and $\log_{10} M_{\rm max}/\hMsun < 13.5$ with and occupation fraction
that scales as $f_{\rm occ}=$. We explore three additional constraints
to narrow down these range: the number of mocks consistent with 
observations, observational constraints on the occupation fraction and
the angular correlation function. These three conditions narrow down
the space parameter to $10.1\leq M_{\rm min}\leq11.0$ and
$10.2\leq M_{\rm max}\leq12.0$, $0.1\leq_{\rm occ}\leq 0.2 $. 
 We make available the mock data for the best models in a public repository. 
 Implications for galaxy formation models? 
\end{abstract}

@@

In our model a dark matter halo can only host one or zero LAE. 
There are three parameters in the model that decide whether a halo can host a
galaxy or not: the lower and upper bounds for the mass range $M_{\rm min}<
M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
  occ}$ of such halos that effectively host a LAE. We do not assign a
luminosity to each LAE. We are primaraly interested in
constraining the halo mass range hosting detectable LAEs under the
conditions defined by \cite{Yamada2012}. In what follows will describe by
the letter ${\mathcal M}$ a model defined by an specific choice of the
three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ y $f_{\rm occ}$.

@@

The measurementens presented in \citep{Yamada2012} do not present a
new measurement of the angular correlation function (ACF). However
\citep{Hayashino2004} performed such calculation on the LAEs observed
in the densest field of SSA22.
